Pillar 2- Quick Topic Models

### 2019-04-29 Pillar 2 - Tmp Topic Modeling.Rmd

  nstart = 10,
  seed   = 1 : 10, #must have length nstart
  best   = TRUE,

  burnin = 100,
  iter   = 2000,
  thin   = 2000

@@

```
###Training Models separately
For time constrains, we sometimes need to train the model only on the manuals or the catalogues, for this we add an extra filtering step in the code that filters on `which_texts`.
```{r LDA fit separate, cache = TRUE, eval = TRUE}
#Timing
initial_time <- Sys.time()

@@

@@

#Plot
plot_evaluation("catalogues")
#plot_evaluation("manuals")
```
##Different alphas and delta (prior of term distributions over topics)
To evaluate the impact of the initial alpha and beta on our model, we train the model using different inizialization values for alpha and delta. Note that this is only an inizialisation and the algorithm will try to extimate alpha and beta.
###Alpha
```{r alpha, eval = FALSE}
sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS

>>>>

  nstart = 20,
  seed   = 1 : 20, #must have length nstart
  best   = TRUE,

  burnin = 1000,
  iter   = 6000,
  thin   = 100

@@

```
###Training Models separately
For time constrains, we sometimes need to train the model only on the manuals or the catalogues, for this we add an extra filtering step in the code that filters on `which_texts`.
```{r LDA fit separate, cache = TRUE, eval = TRUE}

#Timing
initial_time <- Sys.time()

@@

```{r time print, eval = T} 
(took_how_long)
```

@@

#Plot
plot_evaluation("catalogues")
#plot_evaluation("manuals")
```
##Best model
We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with mode burns and iterations
```{r best model, eval = F}
load("./Output/catalogues_tmp_topic_model_tibble.RDATA") #do not run this if knitted

catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "35") %>% pull(Model) %>%.[[1]]

best_lda <- LDA(x = catalogue_dtm, 
                model = catalogue_lda, 
                control =  list(
                  nstart = 50,
                  seed   = 1 : 50, #must have length nstart
                  best   = TRUE,
                  burnin = 100,
                  iter   = 10000,
                  thin   = 2000) 
                )

save(best_lda, file = "./Output/catalogues_best_model.RDATA") 
```
##Different alphas and delta (prior of term distributions over topics)
To evaluate the impact of the initial alpha and beta on our model, we train the model using different inizialization values for alpha and delta. Note that this is only an inizialisation and the algorithm will try to extimate alpha and beta.
###Alpha
```{r alpha, eval = FALSE}
sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS
